### 2016-09-05 GPCE2016/sections/Introduction.tex
grammar
Text.

Object interfaces provide support for automatic type-refinement.  In
contrast, in CB special care and verbose explicit type-refinement is
required to produce code that deals with subtyping adequately. We
believe that such verbosity hindered and slowed down the discovery of
useful programming patterns involving type-refinement. A recently
discovered solution~\cite{eptrivially} to the Expression
Problem~\cite{wadler98expression} in Java-like languages shows how
easy it is to solve the problem using only type-refinement. However it
took nearly 20 years since the formulation of the problem for that
solution to be presented in the literature. In IB, due to its emphasis
on type-refinement, that solution should have been more obvious.

@@

IB could be explained by defining a novel language, with new syntax
and semantics. However, this would have a steep learning curve.  We
take a different approach instead. For the sake of providing a more
accessible explanation, we will embed our ideas directly into Java.
Our IB embedding relies on the
new features of Java 8: interface \emph{static methods} and
\emph{default methods}, which allow interfaces to have method
implementations. In the context of Java, what we propose is a programming
style, where we never use classes (more precisely, we never
  use the \Q@class@ keyword).  We call this restricted version of
Java \emph{Classless Java}.

@@

\item {\bf Applications and case studies:} we illustrate the usefulness of IB
  through various examples and case studies. The implementation, case
  studies, and an extended
  technical report with a formal translation to Java are 
  online:

{\footnotesize \url{https://github.com/YanlinWang/classless-java}}

>>>>

Object interfaces provide support for automatic type-refinement.  In
contrast, in CB special care and verbose explicit type-refinement are
required to produce code that deals with subtyping adequately. We
believe that such verbosity hindered and slowed down the discovery of
useful programming patterns involving type-refinement. A recently
discovered solution~\cite{eptrivially} to the Expression
Problem~\cite{wadler98expression} in Java-like languages shows how
easy it is to solve the problem using only type-refinement. However it
took nearly 20 years since the formulation of the problem for that
solution to be presented in the literature. In IB, due to its emphasis
on type-refinement, that solution should have been more obvious.

@@

IB could be explained by defining a novel language, with new syntax
and semantics. However, this would have a steep learning curve.  We
take a different approach instead. For the sake of providing a more
accessible explanation, we will embed our ideas directly into Java.
Our IB embedding relies on the
new features of Java 8: interface \emph{static methods} and
\emph{default methods}, which allow interfaces to have method
implementations. In the context of Java, what we propose is a programming
style, where we never use classes (more precisely, we never
  use the \Q@class@ keyword).  We call this restricted version of
Java \emph{Classless Java}. \textcolor{red}{Classless Java provides us
with a way to address the famous diamond problem~\cite{bracha90mixin,Sak89dis}
based on Java 8's interface model: interfaces can offer different implementations
using the default methods, whereas conflicts are supposed to be explicitly resolved,
otherwise the program will be rejected by the compiler. An interface that inherits
a few default implementations of a method from its supertypes can define a new implemention
to hide the conflicts among them, or use the \Q@super@ keyword to specify the one it wants. Examples
and more discussion will be presented afterwards.}

@@

\item {\bf Applications and case studies:} we illustrate the usefulness of IB
  through various examples and case studies. The implementation, case
  studies, and an extended
  technical report with a formal translation to Java are
  online. \footnote{\url{https://github.com/YanlinWang/classless-java}}

### 2016-09-05 GPCE2016/sections/Overview.tex
Text.

>>>>

\textcolor{red}{Note that we are breaking the naming conventions for getters and setters in Java;
they have the same names as their fields in our case, which makes code more concise,
but also presents a nice form of fluent setters with method chaining (see Section~\ref{sec:dsls}).
Fluent setters are useful, and the difference from \Q@with-@ methods is that they do not create new objects.}
